\def\pOneProgress{0}
\def\pTwoProgress{0}
\def\pThreeProgress{44}
\def\pFourProgress{31}

\newcommand\pOneCmpData{
    {}/0
}

\newcommand\pTwoCmpData{
    {Atmega programming.}/0,
    {Depth analysis research.}/0,
    {Driver control analysis using espcam.}/0
}

\newcommand\pThreeCmpData{
    {Start learning about system design.}/40,
    {Start setting up app architecture.}/70,
    {Research on TCP.}/50,
    {Establish live feed from esp CAM.}/60,
    {Establish connection with two esp32.}/0
}

\newcommand\pFourCmpData{
    {CAD Design of Implementable Core Block.}/100,
    {CAD Design of Exhaust Branches.}/0,
    {Core Block Mount Base Plate.}/0,
    {Core Block Mount Top Cover.}/0,
    {Reservoir Connectors.}/0,
    {Drill Holes for Reservoir.}/0,
    {Drill Holes for Electronics Bay.}/0,
    {Drill Holes for Top Hatch.}/0,
    {Drill Holes for Core Block Mount.}/0,
    {Start Working on Painting the Frame.}/100,
    {CAD design of core block panels.}/100,
    {CAD design of core block and exhaust branches interface.}/100,
    {CAD design of exhaust branches.}/0,
    {CAD design of mid layer (with PVC foam) for incubator area.}/0,
    {CAD design of mid layer (with polycarbonate) for incubator area base.}/0,
    {Mark and cut foam pieces for incubator area mid layer.}/0,
    {Start assembling foam mid layer.}/0,
    {Start building core block.}/0,
    {CAD design of AMC.}/25,
    {Prime the frame.}/0,
    {Paint the frame.}/25,
    {Map out auxillary system control and feeback lines.}/100,
    {List out immediately needed components for emcu.}/100,
    {Place orders.}/100
}

